# Hotel Bookings

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("assignment/hotel_stays.RData")

set.seed(42)
library(tidyverse)
library(sessioninfo)
library(tidymodels)
library(caret)
```

The data set consists of `r format(nrow(hotel_stays), big.mark = ",")` data points collected by [Antonio, de Almeida, and Nunes (2019)](https://doi.org/10.1016/j.dib.2018.11.126) regarding hotel bookings. 

We'll try to predict whether the reservation includes children or not. The reference contains information on the variables in the data and the outcome column (`children`) is encoded as a factor. Apart from the reference, you can email me (`mxkuhn@gmail.com`) if you have other questions about the data. The data are in the `assignment` path of this repo.

The assignment is to use tidymodels to

* Split the data so that 75% going into training and 25% is for testing. 

* Try a few models and feature engineering methods to improve the area under the ROC curve.

* Use some sort of out-of-sample technique (e.g. validation set, cross-validation, bootstrap, etc.) to compare models prior to using the test set. 

* Pick a model and evaluate the test set. 

* [optional] Make a PR into this repo's assignment directory to show you results. 

Remember to set random number seeds to make the results reproducible and use `sessioninfo::session_info()` in your code to report your versions. 

```{r train}
train_idx <- createDataPartition(hotel_stays$children, p = .75, list = FALSE)
hotel_train <- hotel_stays[train_idx,]
hotel_test <- hotel_stays[-train_idx,]

hotel_rec <- recipe(children ~ ., data = hotel_train) |>
  step_dummy(all_nominal_predictors())

log_mod <- 
  logistic_reg(penalty = 0.1, mixture = 0.5) |>
  set_engine("glmnet")

glmnet_wflow <- 
  workflow() |>
  add_model(log_mod) |>
  add_recipe(hotel_rec)

glmnet_fit <- fit(glmnet_wflow, data = hotel_stays)
glmnet_fit |> tidy() |> filter(estimate != 0)
```

```{r test}
hotel_aug <- augment(glmnet_fit, hotel_test)

hotel_aug |> 
  roc_curve(truth = children, .pred_yes) |>
  autoplot()
```

